Supporting Information

### 2017-07-07 portfolio/text/supp.Rnw
Stop using minus signs in equations
And add appropriate notes in the captions

\documentclass[12pt]{article}
\usepackage{geometry}
\geometry{verbose, letterpaper, tmargin = 2.54cm, bmargin = 2.54cm,
  lmargin = 2.54cm, rmargin = 2.54cm}
\geometry{letterpaper}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{setspace}
\usepackage{booktabs}
% \usepackage{verbatim}
\usepackage{amsmath}
\usepackage{url}
\usepackage{mathtools}
% \usepackage{lineno}
% \usepackage{xcolor}
% \renewcommand\linenumberfont{\normalfont\tiny\sffamily\color{gray}}
% \modulolinenumbers[2]

@@

\linenumbers

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=5in]{stan-main-effects.pdf}
\caption{Main effects from the hierarchical model
predicting revenue ($\beta$) and variability ($\gamma$) in revenue.
The $\eta$ coefficients represent strategy-level predictors
relating mean species diversity and mean days fished
within a strategy
(both centered by their means and divided by
two times their standard deivations)
to the magnitude of residual error.}
\label{fig:fe}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1.06\textwidth]{stan-str-posteriors-dot.pdf}
\caption{Estimates of within-strategy effects from the hierarchical model.
Panels refer to parameters in equations \ref{eq:mean} and \ref{eq:cv}.
Shown are medians (dots) and 50\% and 95\% credible intervals
(thick and thin line segments).
Strategies are ordered from high to low mean
species diversity from top to bottom.}
\label{fig:re}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1.05\textwidth]{stan-offset-break-anti-spaghetti.pdf}
\caption{Effects of (A) generalizing and (B) specializing from year-to-year for
  individual permit holders \emph{within} the \Sexpr{nstr} most common
  strategies. Changing species diversity from year-to-year is associated with
  higher variability for individuals within the strategies above the zero line.
  Generalizing (A) or specializing (B) is associated with greater expected
  revenue ratios to the right of the zero line and lower expected revenue ratios
  to the left of the zero line. These effects are estimated holding fishing
  season length constant from year-to-year. Dots and line segments represent
  medians and 50\% credible intervals of posteriors. Panel B and Fig.~4 are the
  same.}
\label{fig:mirror}
\end{center}
\end{figure}

>>>>

\documentclass[12pt]{article}
\usepackage{geometry}
\geometry{verbose, letterpaper, tmargin = 2.54cm, bmargin = 2.54cm,
  lmargin = 2.54cm, rmargin = 2.54cm}
\geometry{letterpaper}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{setspace}
\usepackage{booktabs}
% \usepackage{verbatim}
% \usepackage{amsmath}
\usepackage{url}
% \usepackage{mathtools}
% \usepackage{lineno}
% \usepackage{xcolor}
% \renewcommand\linenumberfont{\normalfont\tiny\sffamily\color{gray}}
% \modulolinenumbers[2]

@@

% \linenumbers

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=5in]{stan-main-effects.pdf}
\caption{Main effects from the hierarchical model
predicting revenue ($\beta$) and variability ($\gamma$) in revenue.
The $\eta$ coefficients represent strategy-level predictors
relating mean species diversity and mean days fished
within a strategy
(both centered by their means and divided by
two times their standard deivations)
to the magnitude of residual error.
Note that $\mu_{\beta_1}$, $\beta_4$, $\mu_{\gamma_1}$, and $\gamma_4$
have been multiplied by $-1$
to make these coefficients interpretable as effects of
increasing specialization (as opposed to decreasing specialization).
}
\label{fig:fe}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1.06\textwidth]{stan-str-posteriors-dot.pdf}
\caption{Estimates of within-strategy effects from the hierarchical model.
Panels refer to parameters in equations \ref{eq:mean} and \ref{eq:cv}.
Shown are medians (dots) and 50\% and 95\% credible intervals
(thick and thin line segments).
Strategies are ordered from high to low mean
species diversity from top to bottom.
Note that $\gamma_{1,j}$ and $\beta_{1,j}$ have been multiplied by $-1$
to make these coefficients interpretable as effects of
increasing specialization (as opposed to decreasing specialization).}
\label{fig:re}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1.05\textwidth]{stan-offset-break-anti-spaghetti.pdf}
\caption{Effects of (A) generalizing and (B) specializing from year-to-year for
  individual permit holders \emph{within} the \Sexpr{nstr} most common
  strategies. Changing species diversity from year-to-year is associated with
  higher variability for individuals within the strategies above the zero line.
  Generalizing (A) or specializing (B) is associated with greater expected
  revenue ratios to the right of the zero line and lower expected revenue ratios
  to the left of the zero line. These effects are estimated holding fishing
  season length constant from year-to-year. Dots and line segments represent
  medians and 50\% credible intervals of posteriors. Panel B and Fig.~4 are the
  same.
This is a bivariate display of the $\gamma_{1,j}$, $\gamma_{2,j}$, $\beta_{1,j}$,
  and $\beta_{2,j}$ coefficient estimates displayed in Fig.~\ref{fig:re}.
  Note that $\gamma_{1,j}$ (panel B vertical axis) and $\beta_{1,j}$ (panel B
  horizontal axis) have been multiplied by $-1$ to make these coefficients
  interpretable as effects of increasing specialization (as opposed to
  decreasing specialization).
  }
\label{fig:mirror}
\end{center}
\end{figure}
